%-------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------
 
\documentclass{resume} % Use the custom resume.cls style 

\newcommand{\email}{anader@anahuac.mx}
% \newcommand{\email}{hi@anader.xyz}
\newcommand{\emailLink}{\href{mailto:\email}{\email}}
\newcommand{\tel}{+525525307307}
\newcommand{\telPrint}{+52~55~2530~7307}
\newcommand{\telLink}{\href{tel:\tel}{\telPrint}}

\name{Alfredo Nader Zavala} % Your name 
\address{%
    Mexico City, Mexico\qquad%
    {\telLink}\qquad%
    {\emailLink}%
}

\begin{document}

%-----------------------------------
%   EDUCATION SECTION
%-----------------------------------

\begin{rSection}{ Education }

{\bf{Exchange Studies in Applied Computer Science}} \hfill{Mar 2026 -- Aug 2026}
\\
Faculty of Business Informatics \& Applied Computer Science, Otto-Friedrich-Universität Bamberg, Germany

{\bf{Minor in User Interfaces (UI) and Experience Design (XD)}} \hfill{Jan 2025 -- Dec 2028}
\\
Faculty of Design, Anáhuac University, Mexico City, Mexico

{\bf Bachelor of Engineering in Systems and Information Technology} \hfill {Aug 2023 -- Dec 2028}
\\ 
Faculty of Engineering, Anáhuac University, Mexico City, Mexico

{\bf{International Baccalaureate (IB) Certificate}} \hfill{Aug 2021 -- Jul 2023}
\\
Eton School Mexico, Mexico City, Mexico

{\bf Higher Secondary Certificate (HSC), Class 2023} \hfill {Aug 2020 -- Jul 2023}
\\ 
Eton School Mexico, Mexico City, Mexico

\end{rSection}

%-----------------------------------
%	TECHNICAL STRENGTHS
%-----------------------------------

\begin{rSection}{ Skills and Interests }

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }  
    Skills & Analytical Skills, Business Strategy, Data Analysis, Project Management, Social Media
        \\& Communications, Software Architecture, Software Design, Software Infrastructure,
        \\& Web Design, Web Engineering \\
    Interests & Business Engineering, Combinatorics, Experience Design, Full-Stack Development, Human 
        \\& Behavior, Language Learning (currently studying German, French, and Portuguese), 
        \\& Number Theory, Programming, Software Engineering, Sports, UI, UX \\
    Programming & Arduino, BASIC, C, C++, CSS, GAMBAS, HTML, Java, JavaScript, \LaTeX, Mathematica, \\
    Languages & MongoDB, NextJS, PHP, Python, Shell, SQL, TypeScript
\end{tabular}   

\end{rSection}

%-----------------------------------
%	LANGUAGES
%-----------------------------------

\begin{rSection}{ Languages }

{\bf{Spanish}} \\ Native Language

{\bf{English}} \\ Second Language

{\bf{Italian}} \\ Professional Working Proficiency

\end{rSection}  

%-----------------------------------
%	EXPERIENCE
%-----------------------------------

\begin{rSection}{ Experience }

{\bf Data Analyst at \hfref{https://mindnic.net/}{Mindnic}} \hfill {Nov 2024 -- Feb 2025}
\begin{itemize}
    \item Executed social listening strategies to monitor public sentiment and track trends across diverse social media platforms, news outlets, and mass media.
    \item Translated large volumes of unstructured data into comprehensive executive presentations, delivering actionable insights to guide client decision-making.
    \item Uncovered communication opportunities and PR risks that would otherwise go unnoticed through manual analysis, enabling clients to optimize their strategic responses.
\end{itemize}

\end{rSection}  

%-----------------------------------
%   RESEARCH PUBLICATIONS 
%-----------------------------------

\begin{rSection}{ Research Publication } \itemsep -3pt

{Nader, A. (2024, January 8). \textit{Closed-Form Formula for the Partition Function and Related Functions}\\
(\href{https://doi.org/10.48550/arXiv.2401.04026}{arXiv:2401.04026}). arXiv. \href{https://doi.org/10.48550/arXiv.2401.04026}{https://doi.org/10.48550/arXiv.2401.04026}}
 
\end{rSection}

%-----------------------------------
%	HONORS & AWARDS
%-----------------------------------

\pagebreak
\begin{rSection}{ Honors and Awards }

{\bf 1st Place in the 5th Alan Turing National Programming Contest } \hfill {Dec 2022}
\\ 
Issued by Anáhuac University

{\bf Premio Contacto Banxico} \hfill {Dec 2021}
\\ 
Issued by Banco de México

\end{rSection}  

%-----------------------------------
%	PROJECTS
%-----------------------------------

\begin{rSection}{ Projects }

\href{https://www.anader.xyz}{{\bf Personal Porfolio Website} \hfill {Dec 2025 -- Present}}
\\ 
I needed a place to display all my work, experiences, and blog entries. That's why I created my portfolio website. It has been the perfect place to practice web design and development, UX, and copywriting. The website is hosted at \href{https://www.anader.xyz}{anader.xyz}.

\href{https://estudio.so}{{\bf estudio.so} \hfill {Dec 2024 -- Present}}
\\ 
Teachers (at all levels) often have many administrative responsibilities. Sometimes, these duties can lead to a decline in the quality of their teaching. I am building several software tools so that teachers can focus their time and energy on what matters: providing quality education. Teaching should be about teaching, not about managing.

\end{rSection} 

%-----------------------------------
%	LICENCES & CERTIFICATIONS
%-----------------------------------

\begin{rSection}{ Certifications }

\href{https://learn.nvidia.com/certificates?id=20dOe3VLR0eJb3_a2viC2g}{%
    {\bf{Adding New Knowledge to LLMs}} \hfill{Mar 2026}
    \\
    Issued by NVIDIA; Credential ID 20dOe3VLR0eJb3\_a2viC2g
}

\href{https://learn.nvidia.com/certificates?id=ekCku9j-T1yL3tKTtTiwbA}{%
    {\bf{Building LLM Applications With Prompt Engineering}} \hfill{Nov 2025}
    \\
    Issued by NVIDIA; Credential ID ekCku9j-T1yL3tKTtTiwbA
}

\href{https://learn.nvidia.com/certificates?id=jGHnzwTDRTSHNq5Gg6cX1Q}{%
    {\bf{Fundamentals of Accelerated Data Science}} \hfill{Nov 2025}
    \\
    Issued by NVIDIA; Credential ID jGHnzwTDRTSHNq5Gg6cX1Q
}

\end{rSection}

%-----------------------------------
%   CONTACT
%-----------------------------------

\begin{rSection}{ Contact }

\href{mailto:\email}{\faEnvelope\quad\email}

\href{tel:\tel}{\faPhone\quad\telPrint}

\href{tel:+4915567218118}{\faPhone\quad{+49~155~67218118}}

\href{https://www.anader.xyz}{\faEarthAmericas\quad\0anader.xyz}

\href{https://github.com/Freddy-Nader}{\faGithub\quad\0Freddy-Nader}

\href{https://www.linkedin.com/in/alfredo-nader/}{\faLinkedin\quad\0Alfredo-Nader}

\end{rSection}

\end{document}
