%-------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%-------------------------------------------------
 
\documentclass{resume} % Use the custom resume.cls style 

\newcommand{\email}{anader@anahuac.mx}
% \newcommand{\email}{hi@anader.xyz}
\newcommand{\emailLink}{\href{mailto:\email}{\email}}
\newcommand{\tel}{+525525307307}
\newcommand{\telPrint}{+52~55~2530~7307}
\newcommand{\telLink}{\href{tel:\tel}{\telPrint}}

\name{Alfredo Nader Zavala} % Your name 
\address{%
    Mexico City, Mexico\qquad%
    {\telLink}\qquad%
    {\emailLink}%
}

\begin{document}

%-----------------------------------
%   EDUCATION SECTION
%-----------------------------------

\begin{rSection}{ Education }

{\bf{Minor in User Interfaces (UI) and Experience Design (XD)}} \hfill{Jan 2025 -- Dec 2028}
\\
Faculty of Design, Anáhuac University, Mexico City, Mexico

{\bf Bachelor of Engineering in Systems and Information Technology} \hfill {Aug 2023 -- Dec 2028}
\\ 
Faculty of Engineering, Anáhuac University, Mexico City, Mexico

{\bf{International Baccalaureate (IB) Certificate}} \hfill{Aug 2021 -- Jul 2023}
\\
Eton School Mexico, Mexico City, Mexico

{\bf Higher Secondary Certificate (HSC), Class 2023} \hfill {Aug 2020 -- Jul 2023}
\\ 
Eton School Mexico, Mexico City, Mexico

{\bf Secondary School Certificate (SSC)} \hfill {Aug 2017 -- Jul 2020}
\\ 
Eton School Mexico, Mexico City, Mexico

{\bf Primary Education Certificate} \hfill {Aug 2012 -- Jul 2017}
\\ 
Eton School Mexico, Mexico City, Mexico

\end{rSection}

%-----------------------------------
%	TECHNICAL STRENGTHS
%-----------------------------------

\begin{rSection}{ Skills and Interests }

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{4ex}} l }  
    Skills & Analytical Skills, Business Strategy, Data Analysis, Project Management, Social Media
        \\& Communications, Software Architecture, Software Design, Software Infrastructure,
        \\& Web Design, Web Engineering \\
    Interests & Business Engineering, Combinatorics, Experience Design, Full-Stack Development, Human 
        \\& Behavior, Languages, Number Theory, Programming, Software Engineering, Sports, UI, UX \\
    Programming & Arduino, BASIC, C, C++, CSS, GAMBAS, HTML, Java, JavaScript, \LaTeX, Mathematica, \\
    Languages & MongoDB, NextJS, PHP, Python, Shell, SQL, TypeScript
\end{tabular}   

\end{rSection}

%-----------------------------------
%	LANGUAGES
%-----------------------------------

\begin{rSection}{ Languages }

{\bf{Spanish}} \\ Native Language

{\bf{English}} \\ Second Language

{\bf{Italian}} \\ Professional Working Proficiency

\end{rSection}  

%-----------------------------------
%	EXPERIENCE
%-----------------------------------

\begin{rSection}{ Experience }

{\bf Data Analyst at Mindnic} \hfill {Nov 2024 -- Feb 2025}

{\bf Intern at \href{https://www.ericsson.com}{Ericsson}} \hfill {Nov 2022}

\end{rSection}  

%-----------------------------------
%   RESEARCH PUBLICATIONS 
%-----------------------------------

\begin{rSection}{ Research Publication } \itemsep -3pt        

{Nader, A. (2024, January 8). \textit{Closed-Form Formula for the Partition Function and Related Functions}\\
(arXiv:2401.04026). arXiv. \href{https://doi.org/10.48550/arXiv.2401.04026}{https://doi.org/10.48550/arXiv.2401.04026}}
 
\end{rSection}

%-----------------------------------
%	HONORS & AWARDS
%-----------------------------------

\begin{rSection}{ Honors and Awards }

{\bf 1st Place in the 5th Alan Turing National Programming Contest } \hfill {Dec 2022}
\\ 
Issued by Anáhuac University

{\bf Premio Contacto Banxico} \hfill {Dec 2021}
\\ 
Issued by Banco de México

\end{rSection}  

%-----------------------------------
%	PROJECTS
%-----------------------------------

\begin{rSection}{ Projects }

\href{https://www.anader.xyz}{{\bf Personal Porfolio Website} \hfill {Dec 2025 -- Present}}
\\ 
I needed a place to display all my work, experiences, and blog entries. That's why I created my portfolio website. It has been the perfect place to practice web design and development, UX, and copywriting. The website is hosted at \href{https://www.anader.xyz}{anader.xyz}.

{\bf Ampl} \hfill {Aug 2025 -- Present}
\\ 
Generative AI tools such as ChatGPT, Gemini, and Claude are great… but they all have a flaw: you pay for something you're not getting the most out of. Ampl fixes that: it lets you use all AI models with a pay-as-you-go pricing model, so you stop paying for what you're not using!

{\bf QuickGrading} \hfill {Dec 2024 -- Present}
\\ 
Teachers (at all levels) often have many administrative responsibilities. Sometimes, these duties can lead to a decline in the quality of their teaching. I am building several software tools so that teachers can focus their time and energy on what matters: providing quality education. Teaching should be about teaching, not about managing.

\end{rSection} 

%-----------------------------------
%	LICENCES & CERTIFICATIONS
%-----------------------------------

\begin{rSection}{ Certifications }

\href{https://learn.nvidia.com/certificates?id=ekCku9j-T1yL3tKTtTiwbA}{%
    {\bf{Building LLM Applications With Prompt Engineering}} \hfill{Nov 2025}
    \\
    Issued by NVIDIA; Credential ID ekCku9j-T1yL3tKTtTiwbA
}

\href{https://learn.nvidia.com/certificates?id=jGHnzwTDRTSHNq5Gg6cX1Q}{%
    {\bf{Fundamentals of Accelerated Data Science}} \hfill{Nov 2025}
    \\
    Issued by NVIDIA; Credential ID jGHnzwTDRTSHNq5Gg6cX1Q
}

\end{rSection}

%-----------------------------------
%   CONTACT
%-----------------------------------

\begin{rSection}{ Contact }

\href{mailto:\email}{\faEnvelope\quad\email}

\href{tel:\tel}{\faPhone\quad\telPrint}

\href{https://www.anader.xyz}{\faEarthAmericas\quad\0anader.xyz}

\href{https://github.com/Freddy-Nader}{\faGithub\quad\0Freddy-Nader}

\href{https://www.linkedin.com/in/alfredo-nader/}{\faLinkedin\quad\0Alfredo-Nader}

\end{rSection}

%-----------------------------------
%   DECLARATION
%-----------------------------------

\begin{rSection}{ Declaration}

I hereby declare that all the details furnished above are true to the best of my knowledge and belief.   
  
\end{rSection}

\end{document}
